Monitoring and Projecting Global Hunger: Are We On Track?

### 2021-03-04 docs/modeling_fies.tex
revert to results-first order
Updates from Overleaf

\documentclass{article}

@@

\textit{Keywords: Food Security, Sustainable Development Goal 2, Machine Learning, Food Insecurity Experience Scale, Projections}

@@

\section{Competing Interests}
We have no competing interests to disclose.

>>>>

\documentclass[titlepage]{article}

@@

@@

\section{Additional Information}
All code necessary to reproduce these results is on Github at \href{https://github.com/mcooper/wdl-fies}{github.com/mcooper/wdl-fies}. We have no competing interests to disclose.

### 2021-03-04 docs/modeling_fies_supplement.tex
Updates from Overleaf

\pagestyle{fancy}
\fancyhf{}
\lfoot{Supplemental Materials for \textit{Monitoring and Projecting Global Hunger}}
\rfoot{\thepage}

@@

\begin{center}
\section*{Supplemental Materials for \textit{Monitoring and Projecting Global Hunger}}
\end{center}
\setcounter{table}{0}
\setcounter{figure}{0}
\setcounter{section}{0}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}

>>>>

\pagestyle{fancy}
\fancyhf{}
\lfoot{Supplemental Materials for \textit{Monitoring and Projecting Global Hunger: Are We On Track?}}
\rfoot{\thepage}

@@

\begin{center}
\section*{Supplemental Materials for \textit{Monitoring and Projecting Global Hunger: Are We On Track?}}
\end{center}
\setcounter{table}{0}
\setcounter{figure}{0}
\setcounter{section}{0}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}
